### 2023-04-11 definitions.tex
up
Up

The model we are interested in is WSTS (and later some particular instances, i.e. Timed/Counter Automata for instance).

@@

%A {\em labeled transition system} (LTS for short) is a tuple $\mathscr{S}=(S, \Sigma, \rightarrow)$ where 
%$S$ is a set of {\em states}, $\Sigma$ is a (finite) set of {\em labels}, and 
%${\rightarrow} \subseteq S\times \Sigma \times S$ is a 
%ternary relation,
%denoted as the set of {\em labeled transitions}. 
\end{definition}

%Note 
% that an (unlabeled) transition system can be seen as a labeled transition system where the set of labels consists of only one element.

We prefer to use infix notation and write $s \rightarrow s'$ to denote a {\em transition} from state $s$ to state $s'$ (i.e., $ (s,s') \in  {\rightarrow} $).
We write $\rightarrow^{k}$, $\rightarrow^{+}$, $\rightarrow^{=}$, $\rightarrow^{*}$
for the $k$-step iteration of $\rightarrow$, its transitive closure, its reflexive closure, its reflexive and transitive closure.
Let $X,Y \subseteq S$ and $k \in \mathbb{N}$. We denote $X \longrightarrow^{*} Y$ (resp. $X \longrightarrow^{\leq k} Y$) if from all states $x \in X$ there exists a path (resp. of length smaller than $k$) that reaches a state $y \in Y$.
\noindent
The set of {\em (immediate) successors} of a state $s \in S$ is deﬁned as $\post(s) = \{ s' \in S \mid  ~ s \xrightarrow{} s'\}$. A state without successors is called a {\em dead end}. The set of {\em (immediate) predecessors} of a state $s \in S$ is deﬁned as
$\pred(s) = \{ s' \in S \mid  ~ s' \xrightarrow{} s\}$. \\

@@

We abbreviate $x \leq y \not\leq x$ by $x < y$.
% A partial ordering (a po) is an antisymmetric qo
\alain{Any qo induces an equivalence relation ($x \equiv y$ iff $x \leq y \leq x$).}
% and gives rise to a po between the equivalence classes ?
% 	do we need po ?

@@

In what follows, a downward closed set is represented by its finite set of ideals 
%		$D=\downarrow D$   $I_D=\{J_1, J_2,...,J_n\}$ 		satisfying $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ 
and an upward closed set $U$ is represented by its finite set of minimal elements.
% $M_U$ of its  satisfying $U=\uparrow M_U$.

\alain{est-ce utile et correct ? Let $I,J$ be two upward-closed sets given by its set of minimal element and $D,E$ be two downward-closed sets given by its ideal decomposition. All the four  inclusions $U \subseteq V$,  $U \subseteq D$, $D \subseteq U$ and $D \subseteq E$ are decidable provided that the ordering is decidable.}

% \textcolor{red}{Define WSTS}

% \textcolor{red}{Define SWSTS -  necessary}

@@

% (ii) Given a finite set $A \subseteq S$ with $I =\uparrow A$, we can compute a finite basis $B$ of $I$.
% \alain{(ii) est bizarre car A est déjà une base finie de $\uparrow A$, et $min(A)$ est la base minimale}
%			\end{fact}

For a WSTS $\mathscr{S}$ and an upward closed set $U$, let us study the convergence of the sequence defined by $U_0=U$ and $U_k= U \cup \pred(U_{k-1})$ for $k \geq 1$. When $\mathscr{S}$ has the strong compatibility, the sets $U_k$ are upward closed and $U_k \subseteq U_{k+1}$ so we know that the sequence $(U_k)$ converges. Let us define the \emph{index} of convergence of the sequence $U_k$ as the smallest $k_0$ s.t. $U_k = U_{k_0}$ for all $k \geq k_0$. We then have:  $\pred^*(U) = U_{k_0}$.

@@

>>>>

The model we are interested in is labeled WSTS (and later some particular instances, i.e. Timed/Counter Automata for instance).

@@

\mathieu{ Maybe add this back ?
A {\em labeled transition system} (LTS for short) is a tuple $\mathscr{S}=(S, \Sigma, \rightarrow)$ where 
$S$ is a set of {\em states}, $\Sigma$ is a (finite) set of {\em labels}, and 
${\rightarrow} \subseteq S\times \Sigma \times S$ is a 
ternary relation,
denoted as the set of {\em labeled transitions}. }
\end{definition}

% We prefer to use infix notation and $(s,a ,s')\in {\rightarrow} $ will be abbreviated as    $s  \xrightarrow{a}  s'$ to represent a transition from configuration $s$ to configuration $s'$ with label $a$. 
We prefer to use infix notation and write $s \rightarrow s'$ to denote a {\em transition} from state $s$ to state $s'$ (i.e., $ (s,s') \in  {\rightarrow} $).
We write $\rightarrow^{k}$, $\rightarrow^{+}$, $\rightarrow^{=}$, $\rightarrow^{*}$
for the $k$-step iteration of $\rightarrow$, its transitive closure, its reflexive closure, its reflexive and transitive closure.
Let $X,Y \subseteq S$ and $k \in \mathbb{N}$. We denote $X \longrightarrow^{*} Y$ (resp. $X \longrightarrow^{\leq k} Y$) if from all states $x \in X$ there exists a path (resp. of length smaller than $k$) that reaches a state $y \in Y$.
\noindent
The set of {\em (immediate) successors} of a state $s \in S$ is defined as 
 $\post(s) = \{ s' \in S \mid  ~ s \xrightarrow{} s'\}$. 
% $\post(s) = \{ s' \in S \mid  ~ \exists a \in \Sigma~ s \xrightarrow{a} s'\}$. 
A state without successors is called a {\em dead end}. 
The set of {\em (immediate) predecessors} of a state $s \in S$ is deﬁned as
 $\pred(s) = \{ s' \in S \mid  ~ s' \xrightarrow{} s\}$. 
% $\pred(s) = \{ s' \in S \mid  ~ \exists a \in \Sigma~ s' \xrightarrow{a} s\}$. 
By iterating $\pred$ and $\post$ we obtain
$\post^n(s) = \{ s' \in S \mid  ~ s' \xrightarrow{}^n s\}$
and
$\pred^n(s) = \{ s' \in S \mid  ~ s' \xrightarrow{}^n s\}$.
However, we are generally more interested in
$\post^{\leq n}(s) = \bigcup_{1 \leq i \leq n} \post^i(s)$
and
$\pred^{\leq n}(s) = \bigcup_{1 \leq i \leq n} \pred^i(s)$. \\

@@

We abbreviate $x \leq y \not\leq x$ by $x < y$.
% A partial ordering (a po) is an antisymmetric qo
	% \alain{
Any qo induces an equivalence relation ($x \equiv y$ iff $x \leq y \leq x$).
	% }
% and gives rise to a po between the equivalence classes ?
% 	do we need po ?

@@

In what follows, a downward closed set $D$ is represented by its finite set of ideals 
%		$D=\downarrow D$   $I_D=\{J_1, J_2,...,J_n\}$ 		satisfying $D = \downarrow (J_1 \cup J_2 \cup..\cup J_n)$ 
and an upward closed set $U$ is represented by its finite set of minimal elements. \\
% $M_U$ of its  satisfying $U=\uparrow M_U$.

@@

% (ii) Given a finite set $A \subseteq S$ with $I =\uparrow A$, we can compute a finite basis $B$ of $I$.
% \alain{(ii) est bizarre car A est déjà une base finie de $\uparrow A$, et $\min(A)$ est la base minimale}
%			\end{fact}

For a WSTS $\mathscr{S}$ and an upward closed set $U$, let us study the convergence of the sequence defined by $U_0=U$ and $U_k= U \cup \pred(U_{k-1})$ for $k \geq 1$. When $\mathscr{S}$ has the strong compatibility, the sets $U_k$ are upward closed and $U_k \subseteq U_{k+1}$ so we know that the sequence $(U_k)$ converges. Let us define the \emph{index} of convergence of the sequence $U_k$ as the smallest $k_0$ s.t. $U_k = U_{k_0}$ for all $k \geq k_0$. We then have:  $\pred^*(U) = U_{k_0}$. \\

@@

\noindent
{\bf Vector addition system with states}

% Définir VASS

\begin{definition}
A {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\N^d$-labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em states} of $V$, and where $T \subseteq Q \times \N^d \times Q$ will be referred to as {\em transitions} of $V$. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.
\end{definition}

Subsetquently, $Q \times \N^d$ denotes the set of configurations of $V$.
For every configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z}$.

\mathieu{Defining it like this makes it a LTS rather than a unlabeled TS - maybe talk about how we can 'forget' the labels to obtain an unlabeled TS ?}

When in the context of a $d$-VASS, we denote $0^d$ by $\textbf{0}$.

\problemx{$d$-VASS reachability}
{A $d$-Vass $V=(Q,T)$, and configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$}
{$s \to^* s'$ ? \\}

\problemx{$d$-VASS zero reachability}
{Vass $V=(Q,T)$, $q(\textbf{v}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{v}) \to^* p(\textbf{0})$? \\}

\noindent
{\bf Reset VASS}

A {\em reset ... }
Reset VASS are VASS extended with reset transitions.

\problemx{Reset $d$-VASS reachability}
{A reset $d$-Vass $d$-Vass $V=(Q,T)$, $s,s' \in Q \times \N^d$}
{$s \to^* s'$ ? \\}

\problemx{Reset $d$-VASS zero reachability}
{A reset $d$-Vass $V=(Q,T)$, $q(\textbf{u}) \in Q \times \N^d$}
{$\exists p \in Q ~ q(\textbf{u}) \to^* p(\textbf{0})$? \\}

### 2023-04-11 reachable-resilience.tex
Up

\begin{proposition}\label{reductions}
In WSTS, $t$-liveness is reducible to the state resilience problem.
%	home state and reachability
\end{proposition}

@@

% \alain{rappeler l'idée de la preuve}
The idea behind the proof is the following. For deciding whether a downward-closed set $D$ is reachable from $s$, we check whether
$B_{\uparrow \post^*(s)} \cap D = \emptyset$, \alain{rapeler $B_{\uparrow \post^*(s)}$}  that is equivalent to $\post^*(s)\cap D = \emptyset$ by
Lemma~\ref{Lemma intersection}. For the converse direction, we compute the sequence of upward-closed sets
$U_n = \uparrow post^{\leq n}(s)$ until it becomes stationnary. 
Decidability of downward-reachability leads to the decidability of the following stop condition:
asking whether $S \setminus U_n$ is reachable from $s$.

@@

\begin{proof}
Let us show that Reset VASS, that are effective WSTSs with strong compatibility, don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow \post^*$ for Reset VASS. 
\iffalse
Then, one would be able to decide whether an element $m \in Min(\uparrow \post^*)$ is reachable.
%in counter $i$ 
by examining if there is %some vector $v$ in the basis such that $v(i)=0$
$0$ in the basis%
. But reachability of $0$  %in a counter $i$ 
is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
%	$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\fi
Then, {\sc State-resilience} would be decidable for Reset VASS, which leads to a contradiction.
\end{proof}

@@

\begin{proof}
Let $B_s$ \alain{notation fluctuante} be a basis of $\uparrow \post^*(s)$, $B_\Safe$ a basis of $\Safe$
and $\Bad$ a downward-closed set given by its finite set of (maximal) ideals.
By applying Lemma~\ref{Lemma intersection} twice, we obtain

$$ post^*(s) \cap \Bad \subseteq \pred^*(\Safe) \equiv B_s \cap \Bad \subseteq \pred^*(\Safe)$$
\alain{$\equiv $  ???}

Since $B_s$ is finite and $\Bad$ is decidable, we can directly compute $ B_s \cap \Bad$.
% For every element of $ B_p \cap J$, checking that it is in $\pred^*(I)$ is the same as checking coverability of I, and thus decidable.
We can compute a basis of $\pred^*(\Safe)$ from $B_\Safe$, and hence check that $B_s \cap \Bad \setminus \pred^*(\Safe) = \emptyset$. 
\end{proof}

@@

@@

\begin{proof}
Consider Reset $d$-VASS
in the case $\Safe=\{ \textbf{0} \}$ where  $ \textbf{0} \in \mathbb{N}^d$ 
%			contains only the minimal element $Min(S) = 0$ %$0$ 
\alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$, 
it follows the state-resilience problem \alain{écris toujours pareil les expressions choisies comme state-resilience}is equivalent 
to the problem of whether $0$ can be visited infinitely often. \alain{incompréhensible, explique}
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}

@@

\begin{proof}
Let us suppose that $A \cap U \subseteq D$. Then ${\downarrow (A \cap U)} \subseteq {\downarrow D} = D$. Let us show that $({\downarrow A}) \cap U \subseteq {\downarrow (A \cap U)}$. Let $x \in ({\downarrow A}) \cap U$, then there exists $a \in A$ such that $x \leq a$. Since $x \in U$ and $U$ is downward-closed, we also have $a \in U$ \alain{faux}. Hence $a \in A \cap U$ and then $x \in { \downarrow (A \cap U)}$. In the other direction, since $A \subseteq {\downarrow A}$, the inclusion $({\downarrow  A}) \cap U \subseteq D$ implies $A \cap U \subseteq ({\uparrow  A}) \cap U \subseteq D$.
\end{proof}

@@

\subsection{Synthesis}

Results in the case $\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$:

\noindent
Results in the case $\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$:
\iffalse
(by symmetry) for downward compatible WSTS (but not necessarily upward compatible):

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong downward compatibility ~ & $\downarrow post^*$ effective & both  \\ \hline
   SRP & Undecidable  & Decidable   & Decidable \\ \hline
   BSRP & Undecidable  &  ??  & Decidable \\ \hline
      kSRP & Undecidable  & ?? & Decidable  \\ \hline
 \end{tabular}
\end{center}

\mathieu{Montrer que leurs hypothèses Lossy + $\bot$-bounded + strong upward compatibility c'est plus fort que just strong downward compatibility et $\downarrow \post^*$ effective ?}

Si on ne veut pas s'embêter avec les "downward compatible pas upward compatible" on peut se contenter d'écrire ça plutôt
\fi
%
\alain{tableau trop vide. retirer le dernier tableau et mettre le 1er dans la section correspondate, supprimer section 4.3}
%
\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis &  none  & downward compatible & strongly downward compatible  \\ \hline
   SRP & Undecidable (Thm~\ref{srp down up})  & Decidable (Thm~\ref{downward srp})  & Decidable (Thm~\ref{downward srp}) \\ \hline
   BSRP & ??  &  ??  & Decidable (Prop~\ref{downward brp}) \\ \hline
      kSRP & ??  & ?? & Decidable (Prop~\ref{downward brp}) \\ \hline
 \end{tabular}
\end{center}
% \alain{une hypothèse n'est pas l'ensemble vide}

>>>>

A transition $t$ is live in a configuration $s$ if for each $s' \in \post^*(s)$ there exists a sequence $s''$ with $s' \to^* s''$ such that $t$ is enabled in $s''$.

\problemx{$t$-liveness}
{Vass $V=(Q,T)$, $t \in T$}
{Is $t$ live ?}

\begin{proposition}\label{reductions}
In WSTS, $t$-liveness is reducible to {\sc state-resilience}.
%	home state and reachability
\end{proposition}

@@

% \alain{rappeler l'idée de la preuve}
The idea behind the proof is the following. For deciding whether a downward-closed set $D$ is reachable from $s$, one checks whether
$B_{\uparrow \post^*(s)} \cap D = \emptyset$, 
where $B_{\uparrow \post^*(s)}$ is a basis of $\uparrow \post^*(s)$,
%\alain{rapeler $B_{\uparrow \post^*(s)}$} 
 that is equivalent to $\post^*(s)\cap D = \emptyset$ by
Lemma~\ref{Lemma intersection}. For the converse direction, one computes the sequence of upward-closed sets
$U_n = \uparrow post^{\leq n}(s)$ until it becomes stationnary. 
Decidability of downward-reachability leads to the decidability of the following stop condition:
asking whether $S \setminus U_n$ is reachable from $s$.

@@

\begin{proof}
Let us show that Reset VASS, that are effective WSTSs with strong compatibility, don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow \post^*$ for Reset VASS. 
\iffalse
Then, one would be able to decide whether an element $m \in \min(\uparrow \post^*)$ is reachable.
%in counter $i$ 
by examining if there is %some vector $v$ in the basis such that $v(i)=0$
$0$ in the basis%
. But reachability of $0$  %in a counter $i$ 
is undecidable for Reset VASS. 
% sont WSTS with strong compatibility. et l'accessibilité est undecidable.
%	$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\fi
Then, {\sc State-resilience} would be decidable for Reset VASS, which leads to a contradiction.
\end{proof}

@@

\begin{proof}
Let $B_{\uparrow \post^*(s)}$ 
%\alain{notation fluctuante}
 be a basis of $\uparrow \post^*(s)$, $B_\Safe$ a basis of $\Safe$
and $\Bad$ a downward-closed set given by its finite set of (maximal) ideals.
By applying Lemma~\ref{Lemma intersection} twice, we obtain

$$ \post^*(s) \cap \Bad \subseteq \pred^*(\Safe) \text{ iff } B_{\uparrow \post^*(s)} \cap \Bad \subseteq \pred^*(\Safe)$$
% \alain{$\equiv $  ???}

Since $B_{\uparrow \post^*(s)}$ is finite and $\Bad$ is decidable, we can directly compute $ B_s \cap \Bad$.
% For every element of $ B_p \cap J$, checking that it is in $\pred^*(I)$ is the same as checking coverability of I, and thus decidable.
We can compute a basis of $\pred^*(\Safe)$ from $B_\Safe$, and hence check that $B_{\uparrow \post^*(s)} \cap \Bad \setminus \pred^*(\Safe) = \emptyset$. 
\end{proof}

@@

Results synthesis in the case $\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$:

@@

\begin{proof}
Consider Reset $d$-VASS
in the case $\Safe=\{ \textbf{0} \}$ where  $ \textbf{0} \in \mathbb{N}^d$ 
%			contains only the minimal element $\min(S) = 0$ %$0$ 
\alain{tu n'as pas le doit d'écrire $0$ sans explication}
and $\Bad = \mathbb{N}^d \setminus \Safe$, 
it follows the state-resilience problem \alain{écris toujours pareil les expressions choisies comme state-resilience}is equivalent 
to the problem of whether $0$ can be visited infinitely often. \alain{incompréhensible, explique}
% Since reachability of $0$ is undecidable for Reset VASS, we conclude.
Hence the undecidability.
\end{proof}

@@

\begin{proof}
Let us suppose that $A \cap U \subseteq D$. Then ${\downarrow (A \cap U)} \subseteq {\downarrow D} = D$. Let us show that $({\downarrow A}) \cap U \subseteq {\downarrow (A \cap U)}$. Let $x \in ({\downarrow A}) \cap U$, then there exists $a \in A$ such that $x \leq a$. Since $x \in U$ and $U$ is upward-closed, we also have $a \in U$. Hence $a \in A \cap U$ and then $x \in { \downarrow (A \cap U)}$. In the other direction, since $A \subseteq {\downarrow A}$, the inclusion $({\downarrow  A}) \cap U \subseteq D$ implies $A \cap U \subseteq ({\uparrow  A}) \cap U \subseteq D$.
\end{proof}

@@

### 2023-04-11 resilience-safe-up.tex
details
Up

Let us recall two other results in \cite{BFM-ic17}. Proposition 30 establishes a strong relation between the runs of a WSTS $\mathscr{S}=(S,\rightarrow, \leq)$ and the runs of its completion $\hat{\mathscr{S}}$. It states that if $x \xrightarrow{k} y$ in $\mathscr{S}$ then for every ideal $I \supseteq \downarrow x$, there exists an ideal $J \supseteq \downarrow y$ such that $I \xrightarrow{k} J$ in $\hat{\mathscr{S}}$. Proposition 29 establishes that if $I \xrightarrow{k} J$ in $\hat{\mathscr{S}}$ then for every $y \in J$, there exists $x \in I$ and $y' \geq y$ such that $x \xrightarrow{k'} y'$ in $\mathscr{S}$. Moreover, if $\mathscr{S}$ has transitive compatibility then $k’ \geq k$; if $\mathscr{S}$ has strong compatibility then $k’ = k$.

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two 
%finite \alain{non, confusion entre ensemble et base}
 sets $\Bad = \downarrow \Bad$ and $\Safe = \uparrow \Safe$.
The resilience problem (RP), the bounded resilience problem (BRP)
and the $k$-resilience problem (kRP) are decidable.
\end{theorem}

@@

Hence we obtain: $\mathscr{S}$ is resilient iff for all $i=1,..,n$ and $j= 1,..m$, $\downarrow b_j$ is coverable from ideal $J_i$ in $\hat{\mathscr{S}}$.
%
Let us denote by $k_{i,j}$ the length of a covering sequence that covers $\downarrow b_j$ from $J_i$ in $\hat{\mathscr{S}}$ and let $k_{i,j}\stackrel{\text{def}}{=}\infty$ if $\downarrow b_j$ is not coverable from $J_i$. Let us now define $K_{\mathscr{S}}(\Safe,\Bad)=max(k_{i,j} \mid i=1,..,n$ and $j= 1,..m$).
%	(if all $k_{i,j}$ are finite) else $K=\infty$.
We now have $\mathscr{S}$ is resilient iff $K_{\mathscr{S}}(\Safe,\Bad)$ is finite iff $\mathscr{S}$ is $K_{\mathscr{S}}(\Safe,\Bad)$-resilient with $K_{\mathscr{S}}(\Safe,\Bad)$ finite.

This implies that resilience and bounded resilience are equivalent to coverability.
%
% iff there is a run in $\hat{S}$ from an ideal I to J such that  $\downarrow x \subseteq I$ and $\downarrow b_j \subseteq J$. This is a consequence of  
%Propositions 29 and 30 in \cite{BFM-icalp14} that establish a strong relation between the runs of a WSTS $\mathscr{S}=(S,\rightarrow, \leq)$ with its completion $\hat{S}$.
%' \in I(\Bad)$.
%
%To decide the bounded resilience, we decide $n \times m$ coverability questions: is state $\downarrow b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_{i,j} \mid i=1,..,n $ and $j= 1,..m)$ where $k_{i,j}$ is the least length of a sequence that covers  $\downarrow b_j$ from $J_i$.
%
 % \alain{comment trouver les $k_a$ ?} 
%
%  \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ? il pourrait exister un $K' \geq K$ pour lequel $\mathscr{S}$ est K'-resilient....}. 
%else if some of these $n \times m$ coverability questions are negative then resilience
%do not hold and bounded resilience do not hold either.
Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we deduce that both the 
  resilience problem (RP) and the bounded resilience problem (BRP) are decidable.

@@

	\begin{theorem}\label{k-down-up}
	Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS 
	with strong compatibility and the predbasis hypothesis, and two finite sets: $\Bad$ 
	and $\Safe$.
	The  $k$-resilience problem (kRP) is decidable 
	%	for $k \geq min(K,n)$ where $n$ satisfies $ \uparrow \pred^n(\Safe)=  \uparrow 	\pred^*(\Safe)$. 
	\textcolor{red}{CONJECTURE for now}
	 \end{theorem}

@@

Let us now define $K'_{\mathscr{S}}(\Safe,\Bad)=max(k'_{i,j} \mid i=1,..,n$ and $j= 1,..m$) and we deduce that  $\mathscr{S}$ is $k$-resilient iff $k \geq K'_{\mathscr{S}}(\Safe,\Bad)$.

%	If $k <  min(K,n)$, then we check every path of length smaller
%	than $min(K,n)$ from the ideals of the decomposition of $\Bad$ in the completion \alain{à expliquer mieux}.
\end{proof}

>>>>

Let us recall two other results in \cite{BFM-ic17}. Proposition 30 establishes a strong relation between the runs of a WSTS $\mathscr{S}=(S,\rightarrow, \leq)$ and the runs of its completion $\hat{\mathscr{S}}$. It states that if $x \xrightarrow{k} y$ in $\mathscr{S}$ then for every ideal $I \supseteq \downarrow x$, there exists an ideal $J \supseteq \downarrow y$ such that $I \xrightarrow{k} J$ in $\hat{\mathscr{S}}$. Proposition 29 establishes that if $I \xrightarrow{k} J$ in $\hat{\mathscr{S}}$ then for every $y \in J$, there exists $x \in I$ and $y' \geq y$ such that $x \xrightarrow{k'} y'$ in $\mathscr{S}$. Moreover, if $\mathscr{S}$ has transitive compatibility then $k’ \geq k$; if $\mathscr{S}$ has strong compatibility then $k’ = k$.
%
\alain{definir completion-post-effective. Voir mon papier well behaved....}
%
\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two 
%finite \alain{non, confusion entre ensemble et base}
 sets $\Bad = \downarrow \Bad$ and $\Safe = \uparrow \Safe$.
The resilience problem (RP), the bounded resilience problem (BRP)
and the $k$-resilience problem (kRP) are decidable.
\end{theorem}

@@

Hence we obtain: $\mathscr{S}$ is resilient iff for all $i=1,..,n$ and $j= 1,..m$, $\downarrow b_j$ is coverable from ideal $J_i$ in $\hat{\mathscr{S}}$.
%
Let us denote by $k_{i,j}$ the length of a covering sequence that covers $\downarrow b_j$ from $J_i$ in $\hat{\mathscr{S}}$ and let $k_{i,j}\stackrel{\text{def}}{=}\infty$ if $\downarrow b_j$ is not coverable from $J_i$. Let us now define $K_{\mathscr{S}}(\Safe,\Bad)=\max(k_{i,j} \mid i=1,..,n$ and $j= 1,..m$).
%

%
%	(if all $k_{i,j}$ are finite) else $K=\infty$.
We now have $\mathscr{S}$ is resilient iff $K_{\mathscr{S}}(\Safe,\Bad)$ is finite iff $\mathscr{S}$ is $K_{\mathscr{S}}(\Safe,\Bad)$-resilient with $K_{\mathscr{S}}(\Safe,\Bad)$ finite.

This implies that resilience and bounded resilience are equivalent to coverability.
%
% iff there is a run in $\hat{S}$ from an ideal I to J such that  $\downarrow x \subseteq I$ and $\downarrow b_j \subseteq J$. This is a consequence of  
%Propositions 29 and 30 in \cite{BFM-icalp14} that establish a strong relation between the runs of a WSTS $\mathscr{S}=(S,\rightarrow, \leq)$ with its completion $\hat{S}$.
%' \in I(\Bad)$.
%
%To decide the bounded resilience, we decide $n \times m$ coverability questions: is state $\downarrow b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=\max(k_{i,j} \mid i=1,..,n $ and $j= 1,..m)$ where $k_{i,j}$ is the least length of a sequence that covers  $\downarrow b_j$ from $J_i$.
%
 % \alain{comment trouver les $k_a$ ?} 
%
%  \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ? il pourrait exister un $K' \geq K$ pour lequel $\mathscr{S}$ est K'-resilient....}. 
%else if some of these $n \times m$ coverability questions are negative then resilience
%do not hold and bounded resilience do not hold either.
Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we deduce that both the 
  resilience problem (RP) and the bounded resilience problem (BRP) are decidable.

@@

	\begin{theorem}\label{k-down-up}
	Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS 
	with strong compatibility and the predbasis hypothesis, and two finite sets: $\Bad$ 
	and $\Safe$.
	The  $k$-resilience problem (kRP) is decidable 
	%	for $k \geq \min(K,n)$ where $n$ satisfies $ \uparrow \pred^n(\Safe)=  \uparrow 	\pred^*(\Safe)$. 
	\textcolor{red}{CONJECTURE for now}
	 \end{theorem}

@@

Let us now define $K'_{\mathscr{S}}(\Safe,\Bad)=\max(k'_{i,j} \mid i=1,..,n$ and $j= 1,..m$) and we deduce that  $\mathscr{S}$ is $k$-resilient iff $k \geq K'_{\mathscr{S}}(\Safe,\Bad)$.

%	If $k <  \min(K,n)$, then we check every path of length smaller
%	than $\min(K,n)$ from the ideals of the decomposition of $\Bad$ in the completion \alain{à expliquer mieux}.
\end{proof}
